---
title             : "The title"
shorttitle        : "Title"
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
if(!"papaja" %in% rownames(installed.packages())) {
  devtools::install_github("crsh/papaja")
}
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(readxl)
library(patchwork)
library(arsenal)
knitr::opts_chunk$set(
  fig.height = 6,
  fig.width = 8,
  message = F,
  echo = F,
  warning = F
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  digits = 3
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

my_controls <- tableby.control(
  total = F,
  test = F,
  # No test p-values yet
  numeric.stats = c("meansd", "medianq1q3", "range"),
  cat.stats = c("countpct"),
  stats.labels = list(
    meansd = "Mean (SD)",
    medianq1q3 = "Median (Q1, Q3)",
    range = "Min - Max",
    Nmiss2 = "Missing",
    countpct = "N (%)"
  )
)
```

```{r load_data}
hate_df =
  read_csv(here::here("HateCrimes.csv"),
           col_types =
             "cffdddddd") %>%
  janitor::clean_names() %>%
  drop_na() %>%
  filter(hate_crimes_per_100k_splc < 1.2) %>%
  mutate(across(unemployment:urbanization, as.factor))
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

## Data Description
```{r descriptive, results = "asis"}
hate_df %>%
  select(-state) %>%
  tableby( ~ ., data = ., control = my_controls) %>%
  summary(., title = "Descriptive Statistics",text = TRUE) %>%
  knitr::kable(
    longtable = T,
    caption = "             Summary Statistics, 2016"
  )
```

## Data transformation

## Modeling

### Association

### Adjusting Confounders
```{r slr}
hate_slr =
  hate_df %>%
  mutate(across(where(is.numeric),scale)) %>% 
  nest(.) %>%
  mutate(unemployment =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~ unemployment,
                    data = .x)),
         urbanization =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~ urbanization,
                    data = .x)),
         median_household_income =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~ median_household_income,
                    data = .x)),
         perc_population_with_high_school_degree =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~
                      perc_population_with_high_school_degree,
                    data = .x)),
         perc_non_citizen =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~ perc_non_citizen,
                    data = .x)), 
         gini_index =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~ gini_index,
                    data = .x)),
         perc_non_white =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~ perc_non_white,
                    data = .x)),
         ) %>% 
  select(-data) %>% 
  pivot_longer(everything(),
               names_to = "model",
               values_to = "value") %>% 
  mutate(value = map(value, broom::tidy)) %>% 
  unnest(c(value)) %>% 
  janitor::clean_names() %>%
  filter(term != "(Intercept)") %>% 
  select(-term) %>% 
  mutate(
    lwr = estimate - qt(0.975, 44) * std_error,
    upr = estimate + qt(0.975, 44) * std_error,
    across(where(is.numeric),  ~ as.character(round(.x, 3))),
    `estimate_coefficient_(CI)` =
      str_c(estimate,"(",lwr,",",upr,")",sep = " ")
  ) %>% 
  select(model,`estimate_coefficient_(CI)`,p_value) %>% 
  apa_table(.,
            landscape = TRUE)

hate_slr
```



```{r model,results = "asis"}
hate_md =
  hate_df %>%
  mutate(across(where(is.numeric),scale)) %>% 
  nest(.) %>%
  mutate(model_1 =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~ perc_population_with_high_school_degree,
                    data = .x)),
         model_2 =
           map(.x = data,
               ~ lm(
                 log(hate_crimes_per_100k_splc) ~
                   perc_population_with_high_school_degree + . - state,
                 data = .x
               )),
         model_3 =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~
                      perc_population_with_high_school_degree+gini_index,
                    data = .x)),
         model_4 =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~
                      perc_population_with_high_school_degree * unemployment +
                      gini_index, 
                    data = .x)),
         model_5 =
           map(.x = data,
               ~ lm(log(hate_crimes_per_100k_splc) ~
                      perc_population_with_high_school_degree * urbanization +
                      gini_index,
                    data = .x))) %>% 
  select(-data)

hate_md %>% 
  pivot_longer(model_1:model_3,
               names_to = "model",
               values_to = "value") %>% 
  mutate(value = map(value,broom::tidy)) %>% 
  unnest(c(value)) %>% 
  janitor::clean_names() %>%
  filter(term != "(Intercept)") %>% 
  mutate(
    lwr = estimate - qt(0.975, 44) * std_error,
    upr = estimate + qt(0.975, 44) * std_error,
    across(where(is.numeric),  ~ as.character(round(.x, 3))),
    result =
      str_c(estimate,"(",lwr,",",upr,")",sep = " ")
  ) %>% 
  select(model,term,result) %>% 
  pivot_wider(names_from = model,
              values_from = result) %>% 
  apa_table(.,
            caption = "Association table",
            note = "some note",
            landscape = TRUE)
  
hate_md %>% 
  pivot_longer(model_3:model_5,
               names_to = "model",
               values_to = "value") %>% 
  mutate(value = map(value,broom::tidy)) %>% 
  unnest(c(value)) %>% 
  janitor::clean_names() %>%
  filter(term != "(Intercept)") %>% 
  mutate(
    lwr = estimate - qt(0.975, 44) * std_error,
    upr = estimate + qt(0.975, 44) * std_error,
    across(where(is.numeric),  ~ as.character(round(.x, 3))),
    result =
      str_c(estimate,"(",lwr,",",upr,")",sep = " ")
  ) %>% 
  select(model,term,result) %>% 
  pivot_wider(names_from = model,
              values_from = result) %>% 
  apa_table(.,
            caption = "Model Selection",
            note = "some note",
            landscape = TRUE)
```


# Discussion

## Gini is not a main predictor of Hate crime


## Why income elimiated
(Collinear)


## Limitation


### Sample size


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

# Appendix

```{r correlation，fig.cap = "Correlation Plot"}
hate_df %>% 
  select(where(is.numeric)) %>% 
  cor() %>% 
  corrplot::corrplot(
    method = "circle",
    type = "lower",
    addCoef.col = "black",
    diag = T,
    tl.srt = 45,
    tl.cex = 0.7
  )
```

```{r correlation_orgin, fig.cap = "Original Correlation Plot"}
read_csv(here::here("HateCrimes.csv"),
           col_types =
             "cffdddddd") %>%
  janitor::clean_names() %>%
  drop_na() %>%
  mutate(across(unemployment:urbanization, as.factor)) %>% 
  select(where(is.numeric)) %>% 
  cor() %>% 
  corrplot::corrplot(
    method = "circle",
    type = "lower",
    addCoef.col = "black",
    diag = T,
    tl.srt = 45,
    tl.cex = 0.7
  )
```


```{r log-transformation,fig.cap = "Box-Cox transformation"}
lm(hate_crimes_per_100k_splc ~ . - state,
     data = hate_df) %>% 
  car::boxCox()
```


